---
title: "01-clean-data"
author: "Beatriz Couto Ribeiro"
date: "2024-11-19"
output: html_document
editor_options: 
  chunk_output_type: console
---

# 1. Set Script 

# 0. Clean Environment
```{r}
rm(list = ls())


```



## 1.1. Set Folder
```{r}

getwd()

setwd("C:/Users/wb618493/OneDrive - WBG/Documents/ASA - Privitazation of Distribution/Brazil/Data/DATA_ANEEL")

```


## 1.2. Install and load packages
```{r}

if (!require("pacman")) install.packages("pacman") #pacman will not accept a character vector so the same packages are repeated

pacman::p_load(tidyverse, #packages for data science
               plm, #estimation of linear panel models
               ggplot2,  #creating graphics
               lmtest, #testing linear regression Models
               tseries, #Augmented Dickey-Fuller Test
               clubSandwich, #robustness checks
               sandwich, #robustness checks
               stargazer, #formatting tables for publications
               devtools, #web developer tools 
               rmarkdown, #reproducibility
               tidyr,  #changing the shape and hierarchy of a data set
               dplyr, #grammar of data manipulation
               Synth, #importing and exporting
               SCtools, #extensions for Synthetic Controls Analysis
               MSCMT,  #Multivariate Synthetic Control Method
               gsynth, #generalized Synthetic Control Method
               panelView, #visualize data panels
               httr, # call url
               jsonlite, # use API
               DataExplorer, # Automated Exploratory Data Analysis
               kableExtra, #formatting tables
               webshot, #enable table exportation with kableExtra
               ggrepel, #labels with ggplot
               ggthemes, #different graph themes for ggplot
               ggpubr, #put figures together
               car, # check multicollinearity
               lmtest, # robust standard errors
               #scpi, #  SCM with Multiple Treated Units and Staggered Adoption
               synthdid, # Synthetic Difference in Differences Estimation
               plm, # linear models for panel data
               abind, # Combine Multidimensional Arrays
               readxl, #read xls files
               data.table, # Fast aggregation of large data
               basedosdados,
               bigQueryR,
               googleAuthR,
               readxl, # read excel
               openxlsx) # write xlsx file 


```

# 2. Load Files
# 2.1. SAMP ANEEL Files:
Period: 2003-2024 (ANEEL): https://portalrelatorios.aneel.gov.br/luznatarifa/cativo#!
Period: 1991-2002 (ANEEL):https://www.gov.br/aneel/pt-br/centrais-de-conteudos/relatorios-e-indicadores/tarifas-e-informacoes-economico-financeiras 
```{r}

# Define the file names
file_names <- c(
  "samp_aneel_1991-2002.xlsx",
  "samp_aneel_2003-2007.xlsx",
  "samp_aneel_2008-2011.xlsx",
  "samp_aneel_2012-2015.xlsx",
  "samp_aneel_2016-2020.xlsx",
  "samp_aneel_2021-2023.xlsx"
)

# Read all files into a list and bind them together
samp_data <- lapply(file_names, read_excel)
samp_2003_2023 <- do.call(rbind, samp_data[2:6]) # Exclude the first dataset if needed

```

# 2.2. DEC & FEC ANEEL Files:
Period: 2000-2024 (ANEEL): https://portalrelatorios.aneel.gov.br/indicadoresDistribuicao/indicadoresContinuidadeDECFEC
Period: 1993-2016 (ABRADEE): https://abradee.org.br/planilhas-de-1996-a-2022/
```{r}
dec_fec_2023 <- read_excel("DEC_FEC_Mensal_Distribuidora_2023.xlsx")

dec_fec_2022 <- read_excel("DEC_FEC_Mensal_Distribuidora_2022.xlsx")

dec_fec_2021 <- read_excel("DEC_FEC_Mensal_Distribuidora_2021.xlsx")

dec_fec_2020 <- read_excel("DEC_FEC_Mensal_Distribuidora_2020.xlsx")

dec_fec_2019 <- read_excel("DEC_FEC_Mensal_Distribuidora_2019.xlsx")

dec_fec_2018 <- read_excel("DEC_FEC_Mensal_Distribuidora_2018.xlsx")

dec_fec_2017 <- read_excel("DEC_FEC_Mensal_Distribuidora_2017.xlsx")

dec_fec_2016 <- read_excel("DEC_FEC_Mensal_Distribuidora_2016.xlsx")

dec_fec_2015 <- read_excel("DEC_FEC_Mensal_Distribuidora_2015.xlsx")

dec_fec_2014 <- read_excel("DEC_FEC_Mensal_Distribuidora_2014.xlsx")

dec_fec_2013 <- read_excel("DEC_FEC_Mensal_Distribuidora_2013.xlsx")

dec_fec_2012 <- read_excel("DEC_FEC_Mensal_Distribuidora_2012.xlsx")

dec_fec_2011 <- read_excel("DEC_FEC_Mensal_Distribuidora_2011.xlsx")

dec_fec_2010 <- read_excel("DEC_FEC_Mensal_Distribuidora_2010.xlsx")

dec_fec_2009 <- read_excel("DEC_FEC_Mensal_Distribuidora_2009.xlsx")

dec_fec_2008 <- read_excel("DEC_FEC_Mensal_Distribuidora_2008.xlsx")

dec_fec_2007 <- read_excel("DEC_FEC_Mensal_Distribuidora_2007.xlsx")

dec_fec_2006 <- read_excel("DEC_FEC_Mensal_Distribuidora_2006.xlsx")

dec_fec_2005 <- read_excel("DEC_FEC_Mensal_Distribuidora_2005.xlsx")

dec_fec_2004 <- read_excel("DEC_FEC_Mensal_Distribuidora_2004.xlsx")

dec_fec_2003 <- read_excel("DEC_FEC_Mensal_Distribuidora_2003.xlsx")

dec_fec_2002 <- read_excel("DEC_FEC_Mensal_Distribuidora_2002.xlsx")

dec_fec_2001 <- read_excel("DEC_FEC_Mensal_Distribuidora_2001.xlsx")

dec_fec_2000 <- read_excel("DEC_FEC_Mensal_Distribuidora_2000.xlsx")

dec_1993_2016 <- read_excel("data_DEC_1993-2016.xlsx")

fec_1993_2016 <- read_excel("data_FEC_1993-2016.xlsx")

```

# 2.3. Name harmonization before and after privatization file:
```{r}

df_names <- read.csv("names_before_after_privatization_BR_cnpj_concession_11-19-2024.csv")

```

# 2.4. Inflation data IPCA 
Base dos dados: https://basedosdados.org/dataset/ea4d07ca-e779-4d77-bcfa-b0fd5ebea828?table=f1fd2eb7-467a-403b-8f1c-2de8eff354e6
```{r}
## set the google cloud console ID and project
#basedosdados::set_billing_id("inflation-ipca")

#deflate Tariff with monthly IPCA
#create monthly deflator
#ipca_monthly <- basedosdados::read_sql(query = "SELECT ano, mes, indice, variacao_anual, variacao_doze_meses FROM basedosdados.br_ibge_ipca.mes_brasil")

# ipca_monthly_trans<-ipca_monthly%>%arrange(ano,mes)
# ipca_monthly_trans<-ipca_monthly_trans%>%mutate(deflator93=indice/100)%>%
#   mutate(deflator122023=deflator93[ano==2023 & mes==12]/deflator93)
# ipca_monthly_trans<-ipca_monthly_trans%>%select(ano,mes,deflator122023)
# ipca_monthly_trans <- type.convert(ipca_monthly_trans, as.is = TRUE) 
# 
# colnames(ipca_monthly_trans) <- c("Year", "Month", "deflator122023")
# 
# write.csv(ipca_monthly_trans, "ipca_deflator_monthly.csv", row.names = FALSE)

ipca_monthly_trans <- read.csv("ipca_deflator_monthly.csv")

```


# 3. Data Preparation
## 3.1. SAMP - ANEEL
### 3.1.1. SAMP - ANEEL: Full merge of 2003-2023 data
```{r}

# Perform the rbind to merge the datasets
#samp_2003_2023 <- rbind(samp_2003_2007, samp_2008_2011, samp_2012_2015, 
#                            samp_2016_2020, samp_2021_2023)

```

### 3.1.2. SAMP - ANEEL: format the database samp_1991_2002 to have a similar layout to samp_2003_2023
```{r}

#Convert the date column to Date type
samp_1991_2002$MêsAno <- as.Date(samp_1991_2002$MêsAno)

# Extract the year and month and create new columns
samp_1991_2002 <- samp_1991_2002 %>%
  mutate(
    year = year(MêsAno),
    month = month(MêsAno))

# Remove the "MêsAno" column
samp_1991_2002$MêsAno <- NULL


```

### 3.1.3. SAMP - ANEEL: Change Column Names of both datasets, and create a variable "Tax" in samp_2003_2023, and the "RevenueTax" in samp_1991_2002
```{r}

colnames(samp_1991_2002) <- c("Tension", "Firm", "Class", "Consumers", "ConsumptionEnergy", "Demand", "Revenue", "Tax", "Year", "Month")

colnames(samp_2003_2023) <- c("Firm", "Year", "Month", "Tension", "Class", "ConsumptionEnergy", "Revenue", "RevenueTax", "Consumers")


samp_2003_2023 <- samp_2003_2023 %>% mutate(Tax = RevenueTax - Revenue)

samp_1991_2002 <- samp_1991_2002 %>% mutate(RevenueTax = Tax + Revenue)


# Temporarily removing the variable "Demand" from samp_1991_2002, because it is not clear what this number means
samp_1991_2002$Demand <- NULL

```


### 3.1.4. SAMP - ANEEL: Merging both datasets: samp_2003_2023 and samp_1991_2002
```{r}

# Changing "Year" and "Month" variable to numeric, to enable merging 
samp_2003_2023$Year <- as.numeric(samp_2003_2023$Year)
samp_2003_2023$Month <- as.numeric(samp_2003_2023$Month)


# Perform the rbind to append the datasets
samp_1991_2023<-bind_rows(samp_2003_2023,samp_1991_2002)

```

### 3.1.5. SAMP - ANEEL: Rename Variables
```{r}

print(unique(samp_1991_2023$Tension))

# Tension
samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "B1 - Residencial Baixa Renda(Consumo Mensal Superior ao Limite Regional de 200kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 831 a 1.245 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 591 a 1.135 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 342 a 655 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 137 a 341 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 1.437 a 2.154 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal até 136 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 1.136 a 1.436 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 656 a 830 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 342 a 590 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 237 a 341 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 137 a 236 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1- Baixa Renda - Consumo mensal superior a 30 kWh e inferior ou igual a 100 kWh (RES. 945/2010)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1- Baixa Renda - Consumo mensal superior a 100 kWh e inferior ou igual a 220 kWh (RES. 945/2010)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1- Baixa Renda - Consumo mensal inferior ou igual a 30 kWh (RES. 945/2010)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1- Baixa Renda - Consumo mensal superior a 220 kWh (RES. 945/2010)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda(Consumo Mensal Superior ao Limite Regional de 160kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 161 a 180 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 181 a 200 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 201 a 220 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda(Consumo Mensal Superior ao Limite Regional de 220kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 141 a 150 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda(Consumo Mensal Superior ao Limite Regional de 140kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 101 a 140 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 80 a 100 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal até 30 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda(Consumo Mensal Superior ao Limite Regional de 180kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal superior a 30 kWh e inferior a 80kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 151 a 160 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 1.437 a  2.154 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal de 656 a  830 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal superior a 100 até 200 kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda (Consumo mensal  de 1.136 a  1.436 Ah)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa Renda(Consumo Mensal Superior ao Limite Regional de 150kWh)" ~ "B1 - Residencial Baixa Renda",
    Tension == "B1 - Residencial Baixa" ~ "B1 - Residencial Baixa Renda",
    Tension == "B" ~ "B1",
    Tension == "B1 - Residencial" ~ "B1",
    TRUE ~ Tension
  ))

samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "B4b - Iluminação Pública - Bulbo de Lâmpada" ~ "B4",
    Tension == "B4a - Iluminação Pública - Rede de Distribuição" ~ "B4",
    Tension == "B4c - Iluminação Pública - Nível de IP acima do Padrão" ~ "B4",
    TRUE ~ Tension
  ))

samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "B2 - Rural" ~ "B2",
    Tension == "B2 - Serviço Público de Irrigação" ~ "B2",
    Tension == "B2 - Cooperativa de Eletrificação Rural" ~ "B2",
    TRUE ~ Tension
  ))

samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "A4 (2,3 a 25 kV)" ~ "A4 (2,3 a 25 kV)",
    Tension == "A4 - Cooperativa de Eletrificação Rural (2,3 kV a 25 kV)" ~ "A4 (2,3 a 25 kV)",
    Tension == "A4a - Cooperativa de Eletrificação Rural Tipo 1" ~ "A4 (2,3 a 25 kV)",
    Tension == "A4 - Serviço Público de Irrigação (2,3 kV a 25 kV)" ~ "A4 (2,3 a 25 kV)",
    Tension == "A4b - Cooperativa de Eletrificação Rural Tipo 2" ~ "A4 (2,3 a 25 kV)",
    Tension == "A4c - Cooperativa de Eletrificação Rural Tipo 32" ~ "A4 (2,3 a 25 kV)",
    Tension == "A4c - Cooperativa de Eletrificação Rural Tipo 3" ~ "A4 (2,3 a 25 kV)",
    Tension == "A4" ~ "A4 (2,3 a 25 kV)",
    TRUE ~ Tension
  ))

samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "A2 (88 a 138 kV)" ~ "A2 (88 a 138 kV)",
    Tension == "A2 - Cooperativa de Eletrificação Rural (88 a 138 kV)" ~ "A2 (88 a 138 kV)",
    Tension == "A2  Serviço Público de Irrigação" ~ "A2 (88 a 138 kV)",
    Tension == "A2" ~ "A2 (88 a 138 kV)",
    TRUE ~ Tension
  ))


samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "A3a (30 kV a 44 kV)" ~ "A3a (30 kV a 44 kV)",
    Tension == "A3a - Serviço Público de Irrigação (30 kV a 44 kV)" ~ "A3a (30 kV a 44 kV)",
    Tension == "A3a - Cooperativa de Eletrificação Rural (30 kV a 44 kV)" ~ "A3a (30 kV a 44 kV)",
    Tension == "A3a" ~ "A3a (30 kV a 44 kV)",
    TRUE ~ Tension
  ))
 

samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "A3 ( 69 kV)" ~ "A3 (69 kV)",
    Tension == "A3 - Cooperativa de Eletrificação Rural (69 kV)" ~ "A3 (69 kV)",
    Tension == "A3 - Serviço Público de Irrigação (69 kV))" ~ "A3 (69 kV)",
    Tension == "A3 - Serviço Público de Irrigação (69 kV)" ~ "A3a (30 kV a 44 kV)",
    Tension == "A3" ~ "A3a (30 kV a 44 kV)",
    Tension == "A3 (69 kV)" ~ "A3a (30 kV a 44 kV)",
    TRUE ~ Tension
  ))


samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "B3 - Classe Comercial (Consumo mensal até 820 Ah)" ~ "B3",
    Tension == "B3 - Classe Comercial  (Consumo mensal até 1.436 Ah)" ~ "B3",
    Tension == "B3 - Demais Classes" ~ "B3",
    TRUE ~ Tension
  ))

samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "A1" ~ "A1 (230 kV ou mais)",
    TRUE ~ Tension
  ))   

samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Tension = case_when(
    Tension == "AS (Subterrâneo)" ~ "AS",
    TRUE ~ Tension
  )) 

# Class

print(unique(samp_1991_2023$Class))


samp_1991_2023 <- samp_1991_2023 %>%
  mutate(Class = case_when(
    Class == "Rural Aquicultor" ~ "Rural",
    Class == "Rural Irrigante" ~ "Rural",
    Class == "Comercial" ~ "Commercial",
    Class == "Comercial, Serviços e Outras" ~ "Commercial",
    Class == "Serviço Público (água, esgoto e saneamento)" ~ "Public Service",
    Class == "Serviço Público (tração elétrica)" ~ "Public Service",
    Class == "Consumo Próprio" ~ "Own Consumption",
    Class == "Iluminação Pública" ~ "Public Lighting",
    Class == "Poder Público" ~ "Public Government",
    Class == "Serviço Público" ~ "Public Service",
    Class == "Residencial" ~ "Residential",
    TRUE ~ Class
  )) 


```

### 3.1.6. SAMP - ANEEL: Eliminate lines that start with "Applied filters:" and "NA"
```{r}

samp_1991_2023 <- samp_1991_2023 %>%
  filter(!grepl("^Applied filters:", Firm))

# Check for NA's
samp_1991_2023 <- samp_1991_2023 %>%
  filter(!is.na(Firm))
 
num_na_firm <- sum(is.na(samp_1991_2023$Firm))

```


### 3.1.7. SAMP - ANEEL: Consider inflation on the variables and create a annual database
```{r}

#Create variable Tariff
df_1991_2023 <- samp_1991_2023 %>%
  mutate(Tariff = if_else(!is.na(ConsumptionEnergy) & ConsumptionEnergy>0 ,Revenue / ConsumptionEnergy, NA))

# Left Join with inflation based on "Year" and "Month"
df_joined <- left_join(df_1991_2023, ipca_monthly_trans, by = c("Year" = "Year", "Month" = "Month"))


#Impute monthly values by taking the average consumption of that year

# #Create Tariff 
# df_annual <- df_annual %>%
#   mutate(Tariff = if_else(!is.na(consumption),revenue / consumption, NA))

# Deflate the Tariff variable
df_joined<-df_joined%>%mutate(Tariff_1223_BRL= Tariff*deflator122023,
                              Revenue_1223_BRL=Revenue*deflator122023,
                              revenue_tax_1223_BRL=RevenueTax*deflator122023,
                              tax_1223_BRL=Tax*deflator122023)


# create annual data set
 df_annual <- df_joined %>%
   group_by(Firm, Year, Tension, Class) %>%
   summarize(
     revenue = ifelse(all(is.na(Revenue_1223_BRL)), NA_real_, sum(Revenue_1223_BRL, na.rm = TRUE)),
     revenue_tax = ifelse(all(is.na(revenue_tax_1223_BRL)), NA_real_, sum(revenue_tax_1223_BRL, na.rm = TRUE)),
     consumption= ifelse(all(is.na(ConsumptionEnergy)), NA_real_, sum(ConsumptionEnergy, na.rm = TRUE)),
     consumers = ifelse(all(is.na(Consumers)), NA_real_, sum(Consumers, na.rm = TRUE)),
     tax = ifelse(all(is.na(tax_1223_BRL)), NA_real_, sum(tax_1223_BRL, na.rm = TRUE)))%>%
   mutate(Tariff_1223_BRL=revenue/consumption)


```


### 3.1.8. SAMP - ANEEL: Merge the datasets: "df_names" and "samp_1991_2023_names", and save
```{r}

samp_1991_2023_names <- df_annual %>%
   left_join(df_names, by = c("Firm" = "Before_Privatization"), relationship = "many-to-many") %>%
   mutate(Firm_After = After_Privatization) %>%
   select(-After_Privatization) %>%
   filter(!is.na(Type))  # Exclude rows where Type is NA

# Select the desired columns
#samp_1991_2023_names <- samp_1991_2023_names[, 2:14]

#Change name of the "Firm" column to "Firm_After"
#samp_1991_2023_names <- samp_1991_2023_names %>% rename(Firm = Firm_After)

# Convert all names in the 'Firm' column to uppercase, otherwise some variables will be lost
#samp_1991_2023_names$Firm <- toupper(samp_1991_2023_names$Firm)

# Convert all names in the 'Firm' column to uppercase, otherwise some variables will be lost
##samp_1991_2023_names$Firm <- toupper(samp_1991_2023_names$Firm)

#write.csv(samp_1991_2023, "ANEEL_SAMP_1991-2023.csv", row.names = FALSE)

head(fec_dec_1993_2023)

```


# 3.2.  FEC & DEC - ANEEL: Full merge of 2000-2023 data
```{r}

# Perform the rbind to merge the datasets
dec_fec_2000_2023 <- rbind(dec_fec_2023, dec_fec_2022, dec_fec_2021, 
                        dec_fec_2020, dec_fec_2019, dec_fec_2018,
                        dec_fec_2017, dec_fec_2016, dec_fec_2015,
                        dec_fec_2014, dec_fec_2013, dec_fec_2012,
                        dec_fec_2011, dec_fec_2010, dec_fec_2009,
                        dec_fec_2008, dec_fec_2007, dec_fec_2006,
                        dec_fec_2005, dec_fec_2004, dec_fec_2003,
                        dec_fec_2002, dec_fec_2001, dec_fec_2000)

```


### 3.2.1. FEC & DEC - ANEEL: Eliminate lines that start with "Applied filters:" and "NA"
```{r}

dec_fec_2000_2023 <- dec_fec_2000_2023 %>%
  filter(!grepl("^Applied filters:", Distribuidora))

# Check for NA's
dec_fec_2000_2023_clean <- dec_fec_2000_2023 %>%
  filter(!is.na(Distribuidora))
 
num_na_firm <- sum(is.na(dec_fec_2000_2023_clean$Distribuidora))

print(num_na_firm)

```

### 3.2.2. FEC & DEC - ANEEL: Change Column names, select only concessions and select only some variables
```{r}

# Rename column names
colnames(dec_fec_2000_2023)

colnames(dec_fec_2000_2023) <- c("Firm", "Type", "Year", "Month", "Consumers", "DEC", "FEC", "DECXP", "FECXP", "DECXN", "FECXN", "DECIP", "FECIP", "DECIND", "FECIND",    "DECINE", "FECINE", "DECINC", "FECINC", "DECINO", "FECINO", "DECIPC", "FECIPC", "DECXPC", "FECXPC", "DECXNC", "FECXNC")

dec_fec_2000_2023 <- dec_fec_2000_2023 %>%
  filter(Type!="Permissão")  # remove Permission type

# Select only some columns from the dataset
dec_fec_2000_2023_sel <- dec_fec_2000_2023 %>% select("Firm", "Year", "Month", "DEC", "FEC")


```

### 3.2.3. FEC & DEC - ANEEL: Create a variable with the annual FEC and DEC
```{r}

annual_DEC_FEC <- dec_fec_2000_2023_sel %>%
  group_by(Year, Firm) %>%
  summarise(
    DEC = sum(DEC, na.rm = TRUE),
    FEC = sum(FEC, na.rm = TRUE)
  ) %>%
  ungroup()

# Change columns names
colnames(annual_DEC_FEC) <- c("Year", "Firm", "SAIDI", "SAIFI")

# Convert all names in the 'Firm' column to uppercase
annual_DEC_FEC$Firm <- toupper(annual_DEC_FEC$Firm)

```

### 3.2.4. FEC & DEC - ANEEL: Prepare the DEC & FEC dataset from 1993-2016
```{r}
# Wide to long format
dec_1993_2016_long <- melt(setDT(dec_1993_2016), id.vars = c("EMPRESA"), variable.name = "year")

fec_1993_2016_long <- melt(setDT(fec_1993_2016), id.vars = c("EMPRESA"), variable.name = "year")

# Change columns names
colnames(dec_1993_2016_long) <- c("Firm", "Year", "SAIDI")

colnames(fec_1993_2016_long) <- c("Firm", "Year", "SAIFI")

# Left Join with inflation based on "Year" and "Month"
dec_fec_1993_2016 <- left_join(fec_1993_2016_long, dec_1993_2016_long, by = c("Firm" = "Firm", "Year" = "Year"))

# Convert 'Year' from factor to numeric
dec_fec_1993_2016$Year <- as.numeric(as.character(dec_fec_1993_2016$Year))

# Filter 1993-1999
dec_fec_1993_1999 <- dec_fec_1993_2016 %>%
  filter(Year < 2000)  # remove Permission type

# Convert all names in the 'Firm' column to uppercase
dec_fec_1993_1999$Firm <- toupper(dec_fec_1993_1999$Firm)

# Save the dataset to harmonize the names
#write.csv(dec_fec_1993_1999, "dec_fec_1993_1999.csv", row.names = FALSE)


```


### 3.2.6. FEC & DEC - ANEEL: Harmonize names and include the the Privatization data
```{r}

# Convert all names in the 'Firm' column to uppercase
df_names$Before_Privatization <- toupper(df_names$Before_Privatization)

# Convert the 'Firm' column to UTF-8 encoding to handle any special characters
df_names$After_Privatization <- iconv(df_names$After_Privatization, from = "latin1", to = "UTF-8")

# Convert all names in the 'Firm' column to uppercase
df_names$After_Privatization <- toupper(df_names$After_Privatization)

dec_fec_1993_1999_names <- dec_fec_1993_1999 %>%
  left_join(df_names, by = c("Firm" = "Before_Privatization"), relationship = "many-to-many") %>%
  mutate(Firm_After = After_Privatization) %>%
  select(-After_Privatization) # Optionally remove the After_Privatization column if not needed
  #select(-Firm)


annual_DEC_FEC_names <- annual_DEC_FEC %>%
  left_join(df_names, by = c("Firm" = "Before_Privatization"), relationship = "many-to-many") %>%
  mutate(Firm_After = After_Privatization) %>%
  select(-After_Privatization)  # Optionally remove the After_Privatization column if not needed
  #select(-Firm)

```


### 3.2.5. FEC & DEC - ANEEL: Merge the dataset dec_fec_1993_1999 and annual_DEC_FEC 
```{r}

# Perform the rbind to merge the datasets
fec_dec_1993_2023 <- rbind(dec_fec_1993_1999_names, annual_DEC_FEC_names)


#Change name of the "Firm" column to "Firm_After"
#fec_dec_1993_2023 <- fec_dec_1993_2023 %>% rename(Firm = Firm_After)

```


### 3.2.7. FEC & DEC - ANEEL: Join datasets "samp_1991_2023_names" and "fec_dec_1993_2023"
```{r}


# Select only the required columns from fec_dec_1993_2023 and handle duplicates
fec_dec_selected <- fec_dec_1993_2023 %>%
  select(CNPJ, Year, SAIDI, SAIFI) %>%
  group_by(CNPJ, Year) %>%
  summarise(
    SAIDI = mean(SAIDI, na.rm = TRUE),  # Calculate the average of SAIDI
    SAIFI = mean(SAIFI, na.rm = TRUE),  # Calculate the average of SAIFI
    .groups = "drop"  # Drop the grouping after summarising
  )

# Perform a left join based on CNPJ and Year
merged_dataset <- samp_1991_2023_names %>%
  left_join(fec_dec_selected, by = c("CNPJ", "Year"), relationship = "many-to-many")


```


# Create a dataset to know the companies 
```{r}

  ungroup() %>%                     # Remove existing grouping
  select(Firm, Year, SAIDI) %>% # Select specific columns
  distinct(Firm, Year) %>%          # Remove duplicates based on Firm and Year
  count(Firm) 

```


# 3.3.  Financial DATA - EMIS Next: Full merge of 1996-2023 data
### 3.3.1. EMIS Next: Select the folder where the financial data of the companies are stored
```{r}
setwd("C:/Users/wb618493/OneDrive - WBG/Documents/ASA - Privitazation of Distribution/Brazil/Data/EMIS_financial_indicators_real")

```

### 3.3.2. EMIS Next: Select the main finacial variables 
```{r}

# Function to process each company's file
process_ratios <- function(company_name) {
  # Construct the filename based on the company name
  file_name <- paste0("Company_financials_ratios_", company_name, "_real.xlsx")
  
  # Read the Excel file
  ratios <- read_excel(file_name)
  
  # Select specific rows
  ratios_selc <- ratios[c(8, 18, 55), ]
  
  # Transpose the dataset
  ratios_t <- t(ratios_selc)
  ratios_t <- as.data.frame(ratios_t)
  
  # Change column names
  colnames(ratios_t) <- ratios_t[1, ]
  ratios_t <- ratios_t[-1, ]
  
  # Set desired column names
  colnames(ratios_t) <- c("Year", "netprofit_margin", "debtequity_ratio")
  
  # Add a column with the company name
  ratios_t$Firm <- company_name
  
  # Convert 'Year' column to Date type
  ratios_t$Year <- as.Date(ratios_t$Year, format = "%Y")
  
  # Extract the year into a new column
  ratios_t <- ratios_t %>%
    mutate(Year = year(Year))
  
  # Select the desired columns
  ratios_t <- ratios_t %>%
    select(Year, Firm, netprofit_margin, debtequity_ratio)
  
  return(ratios_t)
}

```

### 3.3.3. EMIS Next: Provide the files names
```{r}

# List of company names
companies <- c("COOPERALIANCA", "AmazonasEnergia", "AMPLA", "ELETROCAR", "CEB", "Ceee", "Celesc", "CELPA", "CELTINS", "CEMAT", "CEMIG", "CERR", "CFLO", "CHESP", "CNEE", "Cocel", "Coelba", "Copel", "Cosern", "Dcelt", "DEMEI", "DMED", "EDEVP", "EDP_ES", "EDP_SP", "EEB", "EFLJC", "EFLUL", "Eletropaulo", "ELFSM", "EnelCE", "EnelSP", "EnergisaAC", "EnergisaBO", "EnergisaMinasRio", "EnergisaNF", "EnergisaPB", "EnergisaRO", "EnergisaSE", "EnergisaSulSudeste", "ENERSUL", "EquatorialAL", "EquatorialCEA", "EquatorialGO", "EquatorialMA", "EquatorialPI", "Forcel", "Hidropan", "Jaguari", "Jari", "LestePaulista", "Light", "Mococa", "Muxfeldt", "Neoenergia_PE", "NeoenergiaBR", "NovaPalma", "Pacto", "Paulista", "Piratininga", "RGE_Sul", "RoraimaEnergia", "SantaCruz", "SULGIPE", "SulPaulista")  # Add more company names as needed

# Loop through each company, process the file, and store in a list
all_ratios <- lapply(companies, process_ratios)

# Combine all the processed data into a single dataset
df_financial_1996_2023 <- bind_rows(all_ratios)

# Split EnergisaSulSudeste into CAIUA (before 2016) and EnergisaSulSudeste (2016 onwards)
df_financial_1996_2023 <- df_financial_1996_2023 %>%
  mutate(Firm = if_else(Firm == "EnergisaSulSudeste" & Year < 2017, "CAIUA", Firm))

# Change the row names to sequential numbers
row.names(df_financial_1996_2023) <- seq_len(nrow(df_financial_1996_2023))

# Convert all names in the 'Firm' column to uppercase
df_financial_1996_2023$Firm <- toupper(df_financial_1996_2023$Firm)

# Convert netprofit_margin and debtequity_ratio to numeric
df_financial_1996_2023 <- df_financial_1996_2023 %>%
  mutate(
    netprofit_margin = as.numeric(gsub("%", "", netprofit_margin)),  # Convert to numeric
    debtequity_ratio = as.numeric(gsub("%", "", debtequity_ratio))   # Convert to numeric
  )

name_check<- merged_data%>%ungroup%>% distinct(Firm)
writexl::write_xlsx(name_check, "test.xlsx")
getwd()
```


### 3.2.6. EMIS Next: Harmonize names and include the the Privatization data
```{r}

# Convert all names in the 'Firm' column to uppercase
df_names$Before_Privatization <- toupper(df_names$Before_Privatization)

# Convert the 'Firm' column to UTF-8 encoding to handle any special characters
df_names$After_Privatization <- iconv(df_names$After_Privatization, from = "latin1", to = "UTF-8")

# Convert all names in the 'Firm' column to uppercase
df_names$After_Privatization <- toupper(df_names$After_Privatization)

df_financial_1996_2023_names <- df_financial_1996_2023 %>%
  left_join(df_names, by = c("Firm" = "Before_Privatization"), relationship = "many-to-many") %>%
  mutate(Firm_After = After_Privatization) %>%
  select(-After_Privatization)  # Optionally remove the After_Privatization column if not needed


```

### 3.2.7. EMIS Next: EMIS Next: Join datasets "merged_dataset" and "df_financial_1996_2023_names"
```{r}
# Select only the required columns from df_financial_1996_2023_names
df_financial_1996_2023_selected <- df_financial_1996_2023_names %>%
  select(CNPJ, Year, netprofit_margin, debtequity_ratio)

# Perform a left join based on CNPJ and Year
merged_dataset_all <- merged_dataset %>%
  left_join(df_financial_1996_2023_selected, by = c("CNPJ", "Year"), relationship = "many-to-many")

write.csv(merged_dataset_all, "C:/Users/wb618493/OneDrive - WBG/Documents/ASA - Privitazation of Distribution/Brazil/Data/merged_dataset_distribution_1991-2023.csv", row.names = FALSE)


```


```{r}

# Step 1: Select relevant columns from each dataset
fec_dec_selected <- fec_dec_1993_2023 %>%
  select(Year, Firm_After, SAIDI, SAIFI)

df_financial_selected <- df_financial_1996_2023_names %>%
  select(Year, Firm_After, netprofit_margin, debtequity_ratio)

# Step 2: Merge datasets
merged_data <- samp_1991_2023_names %>%
  left_join(fec_dec_selected, by = c("Year", "Firm_After")) %>%
  left_join(df_financial_selected, by = c("Year", "Firm_After"))

# Step 3: Summarize in case of duplicates
final_data <- merged_data %>%
  group_by(Year, Firm_After, Tension, Class) %>%
  summarize(
   # Weighted average for SAIDI and SAIFI
    SAIDI = weighted.mean(SAIDI, w = consumers, na.rm = TRUE),
    SAIFI = weighted.mean(SAIFI, w = consumers, na.rm = TRUE),
    # Sum variables
    revenue = sum(revenue, na.rm = TRUE),
    revenue_tax = sum(revenue_tax, na.rm = TRUE),
    consumption = sum(consumption, na.rm = TRUE),
    consumers = sum(consumers, na.rm = TRUE),
    tax = sum(tax, na.rm = TRUE),
    # Average financial metrics
    netprofit_margin = mean(netprofit_margin, na.rm = TRUE),
    debtequity_ratio = mean(debtequity_ratio, na.rm = TRUE),
    .groups = "drop"
  )

# View the final dataset
head(final_data)


```



# 4. Specific Cases
## 4.1. Rede Group
```{r}

# fec_dec_1993_2023_Rede <- fec_dec_1993_2023 %>%
#   mutate(Firm = case_when(
#     Firm == "EQUATORIAL PA" ~ "CELPA",
#     Firm == "ENERGISA ELO" ~ "CFLO",
#     Firm == "ENERGISA BR" ~ "EEB",
#     Firm == "ENERGISA CI" ~ "EnergisaSulSudeste",
#     Firm == "ENERGISA SUL-SUDESTE" ~ "EnergisaSulSudeste",
#     Firm == "ENERGISA VP" ~ "EDEVP",
#     Firm == "ENERGISA NA" ~ "CNEE",
#     Firm == "ENERGISA MS" ~ "ENERSUL",
#     Firm == "ENERGISA MT" ~ "CEMAT",
#     Firm == "ENERGISA TO" ~ "CELTINS",
#     TRUE ~ Firm
#   ))
# 
# 
# fec_dec_1993_2023_Rede <- fec_dec_1993_2023_Rede %>% 
#                               filter(Firm %in% c("CELPA", "CFLO", "EEB", "EnergisaSulSudeste",
#                                                "EDEVP", "CNEE", "ENERSUL", "CEMAT", "CELTINS"))
# 
# 
# # Save the dataset to harmonize the names
# write.csv(fec_dec_1993_2023_Rede, "C:/Users/wb618493/OneDrive - WBG/Documents/ASA - Privitazation of Distribution/Brazil/extract_ANEEL_Tariff_pre2010/ANEEL_ExtractTariff_Pre2010/graph_RedeGroup_SaidiSaifi/fec_dec_1993_2023_RedeGroup.csv", row.names = FALSE)


```




```

