---
title: "02-create-plots"
author: "Beatriz Couto Ribeiro"
date: "2024-11-19"
output: html_document
editor_options: 
  chunk_output_type: console
---

# 0. Clean Environment
```{r}

rm(list = ls())

```



# 1. Set Script 
## 1.1. Set Folder
```{r}

getwd()

setwd("C:/Users/wb618493/OneDrive - WBG/Documents/ASA - Privitazation of Distribution/Brazil/Data/DATA_ANEEL")

```


## 1.2. Install and load packages
```{r}

if (!require("pacman")) install.packages("pacman") #pacman will not accept a character vector so the same packages are repeated

pacman::p_load(tidyverse, #packages for data science
               plm, #estimation of linear panel models
               ggplot2,  #creating graphics
               lmtest, #testing linear regression Models
               tseries, #Augmented Dickey-Fuller Test
               clubSandwich, #robustness checks
               sandwich, #robustness checks
               stargazer, #formatting tables for publications
               devtools, #web developer tools 
               rmarkdown, #reproducibility
               tidyr,  #changing the shape and hierarchy of a data set
               dplyr, #grammar of data manipulation
               Synth, #importing and exporting
               SCtools, #extensions for Synthetic Controls Analysis
               MSCMT,  #Multivariate Synthetic Control Method
               gsynth, #generalized Synthetic Control Method
               panelView, #visualize data panels
               httr, # call url
               jsonlite, # use API
               DataExplorer, # Automated Exploratory Data Analysis
               kableExtra, #formatting tables
               webshot, #enable table exportation with kableExtra
               ggrepel, #labels with ggplot
               ggthemes, #different graph themes for ggplot
               ggpubr, #put figures together
               car, # check multicollinearity
               lmtest, # robust standard errors
               #scpi, #  SCM with Multiple Treated Units and Staggered Adoption
               synthdid, # Synthetic Difference in Differences Estimation
               plm, # linear models for panel data
               abind, # Combine Multidimensional Arrays
               readxl, #read xls files
               data.table, # Fast aggregation of large data
               basedosdados,
               bigQueryR,
               googleAuthR,
               readxl, # read excel
               openxlsx) # write xlsx file 


```


# 2. Load Files
```{r}

df_all <- read.csv("final_data.csv")

df_all <- df_all %>% filter(Year > 1993)

df_all_firms <- read.csv("final_data_firms.csv")

df_all_firms <- df_all_firms %>% filter(Year > 1993)

```


```{r}

# To globally disable scientific notation
options(scipen = 999) 

# Transform the variables from character to numeric
df_all <- df_all %>%
  mutate(
    revenue = as.numeric(revenue),
    revenue_tax = as.numeric(revenue_tax),
    consumption = as.numeric(consumption),
    consumers = as.numeric(consumers),
    SAIDI = as.numeric(SAIDI),
    SAIFI = as.numeric(SAIFI),
    netprofit_margin = as.numeric(netprofit_margin),
    debtequity_ratio = as.numeric(debtequity_ratio))


```


# New variable (before and after privatization)
```{r}

#Create relative time variable (t0= year of privatization)
df_all <- df_all %>%
  group_by(Firm_Final) %>%
  mutate(
    t_privat = if_else(Privatization > 1, Year - Privatization, NA_real_),
    owner_type =if_else(Privatization==0, "state-owned",if_else(Privatization==1, "always private", "privatized")))

```


# firms in each ownership type
```{r}

# Create a bar plot to count the number of firms in each ownership type
df_all %>%  # Group by owner_type and count the number of firms in each category
                group_by(owner_type) %>%
                summarise(count = n_distinct(Firm_Final), .groups = "drop") %>%
  # Plot the results using ggplot2
  ggplot(aes(x = owner_type, y = count, fill = owner_type)) +
  geom_bar(stat = "identity", show.legend = FALSE) +  # Bar plot
  labs(
    title = "Count of Firms by Ownership Type",
    x = "Ownership Type",
    y = "Number of Firms"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

```

# firms privatized by year
```{r}
# Assuming df_priv_count is already prepared
df_priv_count <- df_all %>%
  filter(Privatization > 1) %>%  # Exclude rows where Privatization is 0 or 1
  group_by(Privatization) %>%    # Group by the Privatization year
  summarise(count_firms = n_distinct(Firm_Final), .groups = "drop")  # Count distinct firms privatized each year

# Create the bar plot for privatization counts with customized x-axis breaks
ggplot(df_priv_count, aes(x = Privatization, y = count_firms)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "blue") +  # Bar plot with custom colors
  labs(
    title = "Number of Firms Privatized by Year",
    x = "Year of Privatization",
    y = "Number of Firms Privatized"
  ) +
  scale_y_continuous(
    breaks = seq(0, 10, by = 1),  # Set x-axis breaks from 1995 to 2023 with 3-year intervals
    limits = c(0, 10)             # Ensure the axis spans from 1995 to 2023
  ) +
  scale_x_continuous(
    breaks = seq(1994, 2024, by = 5),  # Set x-axis breaks from 1995 to 2023 with 3-year intervals
    limits = c(1994, 2024)             # Ensure the axis spans from 1995 to 2023
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability
```

# boxplot of SAIDI by Year
```{r}
# Create a boxplot of SAIDI by Year
ggplot(df_all, aes(x = factor(Year), y = SAIDI)) +
  geom_boxplot(fill = "skyblue", color = "blue") +  # Boxplot with custom colors
  labs(
    title = "Annual Distribution of SAIDI",
    x = "Year",
    y = "SAIDI"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )


# Facet by "owner_type"
ggplot(df_all, aes(x = factor(Year), y = SAIDI)) +
  geom_boxplot(fill = "skyblue", color = "blue") +  # Boxplot with custom colors
  labs(
    title = "Annual Distribution of SAIDI",
    x = "Year",
    y = "SAIDI"
  )  +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  ) +
  facet_wrap(~ owner_type)  # Facet by "owner_type"


```


# boxplot of SAIFI by Year
```{r}
# Create a boxplot of SAIDI by Year
ggplot(df_all, aes(x = factor(Year), y = SAIFI)) +
  geom_boxplot(fill = "skyblue", color = "blue") +  # Boxplot with custom colors
  labs(
    title = "Annual Distribution of SAIFI",
    x = "Year",
    y = "SAIFI"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )

# Facet by "owner_type"
ggplot(df_all, aes(x = factor(Year), y = SAIFI)) +
  geom_boxplot(fill = "skyblue", color = "blue") +  # Boxplot with custom colors
  labs(
    title = "Annual Distribution of SAIFI",
    x = "Year",
    y = "SAIFI"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  ) +
  facet_wrap(~ owner_type)  # Facet by "owner_type"

```

# Consumers and Consumption
```{r}

# Summarize the data to calculate annual sums
annual_summary <- df_all %>%
  group_by(Year, owner_type) %>%
  summarise(
    total_consumption = sum(consumption, na.rm = TRUE),  # Sum of annual consumption
    total_consumers = sum(consumers, na.rm = TRUE),     # Sum of annual number of consumers
    .groups = "drop"
  )

# Reshape the data to long format for plotting
annual_long <- annual_summary %>%
  pivot_longer(cols = c(total_consumption, total_consumers), 
               names_to = "Metric", 
               values_to = "Value") %>%
  mutate(Value = Value / 1000000)  # Convert values to thousands

# Create the plot with two lines
ggplot(annual_long, aes(x = Year, y = Value, color = Metric)) +
  geom_line(size = 1) +  # Line plot
  labs(
    title = "Annual Sum of Consumption and Number of Consumers (in Thousands)",
    x = "Year",
    y = "Value (in Thousands)",
    color = "Metric"
  ) +
  scale_color_manual(
    values = c("total_consumption" = "blue", "total_consumers" = "red"),  # Custom line colors
    labels = c("Annual Consumption", "Annual Number of Consumers")       # Legend labels
  ) +
  theme_minimal() +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )+
  facet_wrap(~ owner_type)  # Facet by "owner_type"

```

# Revenue
```{r}

# Summarize the data to calculate annual sums
annual_summary <- df_all %>%
  group_by(Year, owner_type) %>%
  summarise(
    total_revenue = sum(revenue, na.rm = TRUE),  # Sum of annual consumption
    .groups = "drop"
  )

# Reshape the data to long format for plotting
annual_long <- annual_summary %>%
  pivot_longer(cols = c(total_revenue), 
               names_to = "Metric", 
               values_to = "Value") %>%
  mutate(Value = Value / 1000000)  # Convert values to thousands

# Create the plot with two lines
ggplot(annual_long, aes(x = Year, y = Value, color = Metric)) +
  geom_line(size = 1) +  # Line plot
  labs(
    title = "Annual Sum of Revenue (in Thousands)",
    x = "Year",
    y = "Value (in Thousands)",
    color = "Metric"
  ) +
  scale_color_manual(
    values = c("total_revenue" = "blue"),  # Custom line colors
    labels = c("Annual Consumption")       # Legend labels
  ) +
  # scale_x_continuous(
  #   breaks = seq(1994, 2024, by = 5),  # Set x-axis breaks from 1995 to 2023 with 3-year intervals
  #   limits = c(1994, 2024)             # Ensure the axis spans from 1995 to 2023
  # )+
    theme_minimal() +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )+  facet_wrap(~ owner_type)  # Facet by "owner_type"

```



#Annual Average of Debit Equity Ratio
```{r}
# Calculate the annual average of netprofit_margin
annual_avg_debtequity_ratio <- df_all %>%
  group_by(Year, owner_type) %>%
  summarise(
    avg_debtequity_margin = mean(debtequity_ratio, na.rm = TRUE),  # Calculate annual average
    .groups = "drop"
  )

# Create the line graph
ggplot(annual_avg_debtequity_ratio, aes(x = Year, y = avg_debtequity_margin)) +
  geom_line(color = "blue", size = 1) +  # Line for annual average
  geom_point(color = "red", size = 2) +  # Points for each year
  labs(
    title = "Annual Average of Debit Equity Ratio",
    x = "Year",
    y = "Average Debit Equity Ratio"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )+
  facet_wrap(~ owner_type)  # Facet by "owner_type"

```


#Annual Average of Net Profit Margin
```{r}
# Calculate the annual average of netprofit_margin
annual_avg_netprofit_margin <- df_all %>%
  group_by(Year, owner_type) %>%
  summarise(
    avg_netprofit_margin = mean(netprofit_margin, na.rm = TRUE),  # Calculate annual average
    .groups = "drop"
  )

# Create the line graph
ggplot(annual_avg_netprofit_margin, aes(x = Year, y = avg_netprofit_margin)) +
  geom_line(color = "blue", size = 1) +  # Line for annual average
  geom_point(color = "red", size = 2) +  # Points for each year
  labs(
    title = "Annual Average of Net Profit Margin",
    x = "Year",
    y = "Average Net Profit Margin"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )+
  facet_wrap(~ owner_type)  # Facet by "owner_type"

```


# 3. Firm-level Data

# Create the line with Firm_Final and Year for companies that have missing data
```{r}
# Create a reference data frame with all combinations of Firm_Final and Year (1994 to 2023)
complete_years <- data.frame(Year = 1994:2023)
complete_firms <- data.frame(Firm_Final = unique(df_all_firms$Firm_Final))

# Create a full combination of all Firm_Final and Year pairs
complete_grid <- expand.grid(Firm_Final = complete_firms$Firm_Final, Year = complete_years$Year)

# Join with the original data and fill missing rows with NA
df_all_firms_complete <- complete_grid %>%
  left_join(df_all_firms, by = c("Firm_Final", "Year"))

```


#Exclude firms that were always private
```{r}

df_all_firms <- df_all_firms_complete %>%
  filter(Privatization != 1)  # Filters rows where Privatization is not equal to 1

```

# Create Privatization variable referent to the year
```{r}

df_all_firms <- df_all_firms %>%
  mutate(privatization_year = case_when(
    Privatization == 0 ~ "0",  # If Privatization is 0, set intervention to "0"
    Privatization > 1 ~ as.character(if_else(Year >= Privatization, 1, 0))  # If Privatization > 1, set "1" after Privatization year, else "0"
  ))

```

# Create Privatization variable
```{r}

#Create relative time variable (t0= year of privatization)
df_all_firms <- df_all_firms %>%
  mutate(Treatment = case_when(
    Privatization == 0 ~ "control",  # If Privatization is 0, set intervention to "0"
    Privatization > 1 ~ "treated"  # If Privatization > 1, subtract Year from Privatization and convert to character
  ))

```


# Years Before and After
```{r}

df_all_firms <- df_all_firms %>%
  mutate(year_before_after = case_when(
    Privatization == 0 ~ "0",  # If Privatization is 0, set intervention to "0"
    Privatization == 1 ~ "1",  # If Privatization is 1, set intervention to "1"
    Privatization > 1 ~ as.character(Year - Privatization)  # If Privatization > 1, subtract Year from Privatization and convert to character
  ))

```


# Creates a unique numeric identifier for each unique Firm_Final
```{r}

df_all_firms <- df_all_firms %>%
  mutate(idname = dense_rank(Firm_Final)) 

#df_all_firms$Firm_Final <- toupper(df_all_firms$Firm_Final)

```


```{r}

# Reshape the data to long format
df_all_firms_long <- df_all_firms %>%
  pivot_longer(cols = c(SAIDI, SAIFI, debtequity_ratio, revenue, consumers, consumption),
               names_to = "variable", 
               values_to = "value")

# Convert 'year_before_after' to numeric (with negative values allowed)
df_all_firms_long <- df_all_firms_long %>%
  mutate(year_before_after = as.numeric(gsub("[^0-9.-]", "", `year_before_after`)))  # Allow for negative signs


# Calculate the average of each variable for each year
df_all_firms_avg <- df_all_firms_long %>%
  group_by(year_before_after, variable) %>%
  summarise(avg_value = mean(value, na.rm = TRUE), .groups = "drop")

# Plot with geom_line for the average values
ggplot(df_all_firms_avg, aes(x = year_before_after, y = avg_value, color = variable, group = variable)) +
  geom_line() +  # Adds lines for each variable
  facet_wrap(~ variable, scales = "free_y") +  # Creates separate plots for each variable
  labs(
    title = "Average Time Series of Different Variables",
    x = "Year (Before/After)",
    y = "Average Value"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )

```






# 4. Difference-in-difference implementation
```{r OLS Regression Models: PATENT H}

#SAIDI
reg_saidi <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_saidi)

#SAIFI
reg_saifi <- plm(SAIFI ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_saifi)


#PROFIT
reg_profit <- plm(netprofit_margin ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_profit)


#DEBIT
reg_debit <- plm(debtequity_ratio ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_debit)

#consumers
reg_consumers <- plm(consumers ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_consumers)


#consumption
reg_consumption <- plm(consumption ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_consumption)

#revenue
reg_revenue <- plm(revenue ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_revenue)


```

```{r Test: OLS regression OR fixed effect model? - PATENTS H}
#Test for poolability of data: pFtest(PATENTS H)
#all patents h, all controls

did_reg_saidi_with <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "within", 
                 index = c("Firm_Final", "Year"))

did_reg_saidi_pool <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "pooling", 
                 index = c("Firm_Final", "Year"))

pFtest(did_reg_saidi_with,did_reg_saidi_pool)

```

```{r TIME FIXED EFFECTS}
reg_saidi_FEtime <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "within", effect = "time", index = c("Firm_Final", "Year"))
summary(reg_saidi_FEtime)

```

```{r COUNTRY FIXED EFFECTS}
reg_saidi_FEcountry <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "within", effect = "individual", index = c("Firm_Final", "Year"))
summary(reg_saidi_FEcountry)
```

```{r TWO-WAY FIXED EFFECTS}
twoway_H <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ihs_GDPfull + ElecConsumption, data = base, model = "within", effect = "twoway",
                 index = c("country", "Year"))
summary(twoway_H)

twoway_H <- plm(patents_H_application ~ RDI_regulation, data = base, model = "within", 
                effect = "twoway",
                index = c("country", "Year"))
                summary(twoway_H)

```

```{r Testing for FIXED OR RANDOM}
#FIXED
fixed_H <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ElecConsumption + ihs_GDPfull, data=base, index=c("country", "Year"), model="within")
summary(fixed_H)

# Display the fixed effects (constants for each country)
fixef(fixed_H)    

# Testing for fixed effects, null: OLS better than fixed
pFtest(fixed_H, reg_H_app_5)

#RANDOM
random_H <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ElecConsumption + ihs_GDPfull, data=base, index=c("country", "Year"), model="random")
summary(random_H)

#FIXED OR RANDOM: Hausman test
phtest(fixed_H, random_H)

#Testing for time-fixed effects
fixed_H_time <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ElecConsumption + ihs_GDPfull + factor(Year), data=base, index=c("country", "Year"), model="within")
summary(fixed_H_time)

pFtest(fixed_H_time, fixed_H)

plmtest(fixed_H, c("time"), type=("bp"))
#time fixed as well as unit fixed effects are present, hence two-way FE model is to be chosen#

```

```{r Model Test: Serial correlation, heteroskedacity}
#FINAL TWO Way FE Model#
did_reg_H <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ihs_GDPfull + ElecConsumption, data = base, model = "within", effect = "twoway",
                 index = c("country", "Year"))
summary(did_reg_H)

# Pasaran CD (cross-sectional dependence) test reveals NO cross-sectional dependence#
pcdtest(did_reg_H, test = c("cd"))

#Testing for serial correlation, reveals serial correlation!#*
pbgtest(did_reg_H)

#Testing for unit roots/stationarity reveals no unit root present#
Panel.set <- pdata.frame(base, index = c("country", "Year"))

adf.test(Panel.set$patents_H_application, k=2)

#  Breusch-Pagan for heteroskedasticity*
bptest(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ElecConsumption + ihs_GDPfull + factor(country), data = base, studentize=F)

#Estimation with cluster robust standard errors#

coeftest(did_reg_H, 
         vcov = vcovHC(did_reg_H, 
                       method = "arellano",
                       cluster = "group",
                       type="HC0"))

```

