---
title: "02-create-plots"
author: "Beatriz Couto Ribeiro"
date: "2024-11-19"
output: html_document
editor_options: 
  chunk_output_type: console
---

# 0. Clean Environment
```{r}

rm(list = ls())

```



# 1. Set Script 
## 1.1. Set Folder
```{r}

getwd()

setwd("C:/Users/BEATRIZCO/OneDrive - Inter-American Development Bank Group/Documents/INE-WSA/Projects/Privatization Infrastructure/")

```


## 1.2. Install and load packages
```{r}

if (!require("pacman")) install.packages("pacman") #pacman will not accept a character vector so the same packages are repeated

pacman::p_load(tidyverse, #packages for data science
               plm, #estimation of linear panel models
               Rtools,
               ggplot2,  #creating graphics
               lmtest, #testing linear regression Models
               tseries, #Augmented Dickey-Fuller Test
               clubSandwich, #robustness checks
               sandwich, #robustness checks
               stargazer, #formatting tables for publications
               devtools, #web developer tools 
               rmarkdown, #reproducibility
               tidyr,  #changing the shape and hierarchy of a data set
               dplyr, #grammar of data manipulation
               Synth, #importing and exporting
               SCtools, #extensions for Synthetic Controls Analysis
               MSCMT,  #Multivariate Synthetic Control Method
               gsynth, #generalized Synthetic Control Method
               panelView, #visualize data panels
               httr, # call url
               corrplot, #plot correlation graphs
               jsonlite, # use API
               DataExplorer, # Automated Exploratory Data Analysis
               kableExtra, #formatting tables
               webshot, #enable table exportation with kableExtra
               ggrepel, #labels with ggplot
               ggthemes, #different graph themes for ggplot
               ggpubr, #put figures together
               car, # check multicollinearity
               lmtest, # robust standard errors
               #scpi, #  SCM with Multiple Treated Units and Staggered Adoption
               plm, # linear models for panel data
               abind, # Combine Multidimensional Arrays
               readxl, #read xls files
               data.table, # Fast aggregation of large data
               basedosdados,
               bigQueryR,
               googleAuthR,
               readxl, # read excel
               did, #Callway and Santanna DID
               DIDmultiplegt, #Chaisemartin DID
               DIDmultiplegtDYN, # Estimation in Difference-in-Difference Designs with Multiple
               vtable, #summary statistics
               GGally, # ggplot2 extetion
               openxlsx) # write xlsx file 




print(.libPaths())

```


# 2. Load Files
## 2.1. Load dataset
```{r}

df_all <- read.csv("source/final_data.csv")

df_all <- df_all %>% filter(Year > 1996)

df_all_firms <- read.csv("source/final_data_firms.csv")

df_all_firms <- df_all_firms %>% filter(Year > 2002)

```

# 3. Format Dataset
## 3.1. Format: numeric variables
```{r}

# To globally disable scientific notation
options(scipen = 999) 

# Transform the variables from character to numeric
df_all <- df_all %>%
  mutate(
    revenue = as.numeric(revenue),
    revenue_tax = as.numeric(revenue_tax),
    consumption = as.numeric(consumption),
    consumers = as.numeric(consumers),
    SAIDI = as.numeric(SAIDI),
    SAIFI = as.numeric(SAIFI),
    netprofit_margin = as.numeric(netprofit_margin),
    debtequity_ratio = as.numeric(debtequity_ratio))


df_all_firms <- df_all_firms %>%
  mutate(
    netprofit_margin = as.numeric(netprofit_margin))



```


## 2.2. Susbstitution of one value on Net Profit Margin of Copel. Source: https://ri.copel.com/en/sustainability/annual-social-and-environmental-reports/
```{r}

# Net Profit Margin = (Net Profit or Net Income / Total Revenue) x 100% 

# Consolidated Total Revenue = 3,061,009
# Net Profit or Net Income = 475,310

# Official exchange rate (LCU per US$, period average) - Brazil: https://data.worldbank.org/indicator/PA.NUS.FCRF?locations=BR
# 2.35
revenue_copel_2001 <-  3061009/2.35
net_income_copel_2001 <- 475310/2.35

net_profit_copel_2001 <- (net_income_copel_2001/revenue_copel_2001)*100

print(net_profit_copel_2001)

#df_all_firms$netprofit_margin[df_all_firms$Firm_Final == "Copel"] <- 25


df_all_firms[df_all_firms == '-6142700'] <- "15.52789"

```


## 3.2. Create new variable (before and after privatization)
```{r}


df_all_firms <- df_all_firms %>%
  mutate(Privatization = case_when(
    Privatization >= 1995 & Privatization <= 2002 ~ 1,  # Convert to 1
    TRUE ~ Privatization  # Keep other values unchanged
  ))


#Create relative time variable (t0= year of privatization)
df_all_firms <- df_all_firms %>%
  group_by(Firm_Final) %>%
  mutate(
    t_privat = if_else(Privatization > 1, Year - Privatization, NA_real_),
    owner_type =if_else(Privatization==0, "state-owned",if_else(Privatization==1, "always private", "privatized")))

```


## 3.3. Include firms ownership type
```{r}

# Create a bar plot to count the number of firms in each ownership type
df_all_firms %>%  # Group by owner_type and count the number of firms in each category
                group_by(owner_type) %>%
                summarise(count = n_distinct(Firm_Final), .groups = "drop") %>%
  # Plot the results using ggplot2
  ggplot(aes(x = owner_type, y = count, fill = owner_type)) +
  geom_bar(stat = "identity", show.legend = FALSE) +  # Bar plot
  labs(
    title = "Count of Firms by Ownership Type",
    x = "Ownership Type",
    y = "Number of Firms"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

```

# 4. Descriptive Analysis 
## 4.1. Firms privatized by year
```{r}
# Assuming df_priv_count is already prepared
df_priv_count <- df_all_firms %>%
  filter(Privatization > 1) %>%  # Exclude rows where Privatization is 0 or 1
  group_by(Privatization) %>%    # Group by the Privatization year
  summarise(count_firms = n_distinct(Firm_Final), .groups = "drop")  # Count distinct firms privatized each year

# Create the bar plot for privatization counts with customized x-axis breaks
ggplot(df_priv_count, aes(x = Privatization, y = count_firms)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "blue") +  # Bar plot with custom colors
  labs(
    title = "Number of Firms Privatized by Year",
    x = "Year of Privatization",
    y = "Number of Firms Privatized"
  ) +
  scale_y_continuous(
    breaks = seq(0, 10, by = 1),  # Set x-axis breaks from 1995 to 2023 with 3-year intervals
    limits = c(0, 10)             # Ensure the axis spans from 1995 to 2023
  ) +
  scale_x_continuous(
    breaks = seq(2003, 2024, by = 5),  # Set x-axis breaks from 1995 to 2023 with 3-year intervals
    limits = c(2003, 2024)             # Ensure the axis spans from 1995 to 2023
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability
```


## 4.2. boxplot of SAIDI by Year
```{r}
# Create a boxplot of SAIDI by Year
ggplot(df_all_firms, aes(x = factor(Year), y = SAIDI)) +
  geom_boxplot(fill = "skyblue", color = "blue") +  # Boxplot with custom colors
  labs(
    title = "Annual Distribution of SAIDI",
    x = "Year",
    y = "SAIDI"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )


# Facet by "owner_type"
ggplot(df_all_firms, aes(x = factor(Year), y = SAIDI)) +
  geom_boxplot(fill = "skyblue", color = "blue") +  # Boxplot with custom colors
  labs(
    title = "Annual Distribution of SAIDI",
    x = "Year",
    y = "SAIDI"
  )  +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  ) +
  facet_wrap(~ owner_type)  # Facet by "owner_type"


```


## 4.3. boxplot of SAIFI by Year
```{r}
# Create a boxplot of SAIDI by Year
ggplot(df_all_firms, aes(x = factor(Year), y = SAIFI)) +
  geom_boxplot(fill = "skyblue", color = "blue") +  # Boxplot with custom colors
  labs(
    title = "Annual Distribution of SAIFI",
    x = "Year",
    y = "SAIFI"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )

# Facet by "owner_type"
ggplot(df_all_firms, aes(x = factor(Year), y = SAIFI)) +
  geom_boxplot(fill = "skyblue", color = "blue") +  # Boxplot with custom colors
  labs(
    title = "Annual Distribution of SAIFI",
    x = "Year",
    y = "SAIFI"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  ) +
  facet_wrap(~ owner_type)  # Facet by "owner_type"

```

## 4.4. Consumers and Consumption
```{r}

# Summarize the data to calculate annual sums
annual_summary <- df_all_firms %>%
  group_by(Year, owner_type) %>%
  summarise(
    total_consumption = sum(consumption, na.rm = TRUE),  # Sum of annual consumption
    total_consumers = sum(consumers, na.rm = TRUE),     # Sum of annual number of consumers
    .groups = "drop"
  )

# Reshape the data to long format for plotting
annual_long <- annual_summary %>%
  pivot_longer(cols = c(total_consumption, total_consumers), 
               names_to = "Metric", 
               values_to = "Value") %>%
  mutate(Value = Value / 1000000)  # Convert values to thousands

# Create the plot with two lines
ggplot(annual_long, aes(x = Year, y = Value, color = Metric)) +
  geom_line(size = 1) +  # Line plot
  labs(
    title = "Annual Sum of Consumption and Number of Consumers (in Thousands)",
    x = "Year",
    y = "Value (in Thousands)",
    color = "Metric"
  ) +
  scale_color_manual(
    values = c("total_consumption" = "blue", "total_consumers" = "red"),  # Custom line colors
    labels = c("Annual Consumption", "Annual Number of Consumers")       # Legend labels
  ) +
  theme_minimal() +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )+
  facet_wrap(~ owner_type)  # Facet by "owner_type"

```

## 4.5. Revenue
```{r}

# Summarize the data to calculate annual sums
annual_summary <- df_all_firms %>%
  group_by(Year, owner_type) %>%
  summarise(
    total_revenue = sum(revenue, na.rm = TRUE),  # Sum of annual consumption
    .groups = "drop"
  )

# Reshape the data to long format for plotting
annual_long <- annual_summary %>%
  pivot_longer(cols = c(total_revenue), 
               names_to = "Metric", 
               values_to = "Value") %>%
  mutate(Value = Value / 1000000)  # Convert values to thousands

# Create the plot with two lines
ggplot(annual_long, aes(x = Year, y = Value, color = Metric)) +
  geom_line(size = 1) +  # Line plot
  labs(
    title = "Annual Sum of Revenue (in Thousands)",
    x = "Year",
    y = "Value (in Thousands)",
    color = "Metric"
  ) +
  scale_color_manual(
    values = c("total_revenue" = "blue"),  # Custom line colors
    labels = c("Annual Consumption")       # Legend labels
  ) +
  # scale_x_continuous(
  #   breaks = seq(1994, 2024, by = 5),  # Set x-axis breaks from 1995 to 2023 with 3-year intervals
  #   limits = c(1994, 2024)             # Ensure the axis spans from 1995 to 2023
  # )+
    theme_minimal() +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)
  )+  facet_wrap(~ owner_type)  # Facet by "owner_type"

```

## 4.6. Annual Average of Debit Equity Ratio
```{r}
# Calculate the annual average of netprofit_margin
annual_avg_debtequity_ratio <- df_all_firms %>%
  group_by(Year, owner_type) %>%
  summarise(
    avg_debtequity_margin = mean(debtequity_ratio, na.rm = TRUE),  # Calculate annual average
    .groups = "drop"
  )

# Create the line graph
ggplot(annual_avg_debtequity_ratio, aes(x = Year, y = avg_debtequity_margin)) +
  geom_line(color = "blue", size = 1) +  # Line for annual average
  geom_point(color = "red", size = 2) +  # Points for each year
  labs(
    title = "Annual Average of Debit Equity Ratio",
    x = "Year",
    y = "Average Debit Equity Ratio"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )+
  facet_wrap(~ owner_type)  # Facet by "owner_type"

```


## 4.7.Annual Average of Net Profit Margin
```{r}
# Calculate the annual average of netprofit_margin
annual_avg_netprofit_margin <- df_all_firms %>%
  group_by(Year, owner_type) %>%
  summarise(
    avg_netprofit_margin = mean(netprofit_margin, na.rm = TRUE),  # Calculate annual average
    .groups = "drop"
  )

# Create the line graph
ggplot(annual_avg_netprofit_margin, aes(x = Year, y = avg_netprofit_margin)) +
  geom_line(color = "blue", size = 1) +  # Line for annual average
  geom_point(color = "red", size = 2) +  # Points for each year
  labs(
    title = "Annual Average of Net Profit Margin",
    x = "Year",
    y = "Average Net Profit Margin"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )+
  facet_wrap(~ owner_type)  # Facet by "owner_type"

```




# 5. Adapting Dataset for DID
## 5.1. Create Privatization variable referent to the year
```{r}

df_all_firms <- df_all_firms %>%
  mutate(privatization_year = case_when(
    Privatization == 0 ~ "0",  # If Privatization is 0, set intervention to "0"
    Privatization > 1 ~ as.character(if_else(Year >= Privatization, 1, 0))  # If Privatization > 1, set "1" after Privatization year, else "0"
  ))

```

## 5.2. Create Privatization variable
```{r}

#Create relative time variable (t0= year of privatization)
df_all_firms <- df_all_firms %>%
  mutate(Treatment = case_when(
    Privatization == 0 ~ "control",  # If Privatization is 0, set intervention to "0"
    Privatization > 1 ~ "treated"  # If Privatization > 1, subtract Year from Privatization and convert to character
  ))

```

## 5.3. Years Before and After
```{r}

df_all_firms <- df_all_firms %>%
  mutate(year_before_after = case_when(
    Privatization == 0 ~ "0",  # If Privatization is 0, set intervention to "0"
    Privatization == 1 ~ "1",  # If Privatization is 1, set intervention to "1"
    Privatization > 1 ~ as.character(Year - Privatization)  # If Privatization > 1, subtract Year from Privatization and convert to character
  ))

```

## 5.4. Creates a unique numeric identifier for each unique Firm_Final
```{r} 

df_all_firms <- df_all_firms %>%
  group_by(Firm_Final) %>%
  mutate(idname = cur_group_id()) %>%
  ungroup()


#df_all_firms$Firm_Final <- toupper(df_all_firms$Firm_Final)

```

## 5.5. Create the line with Firm_Final and Year for companies that have missing data
```{r}

# Create a reference data frame with all combinations of Firm_Final and Year (1994 to 2023)
complete_years <- data.frame(Year = 1994:2023)
complete_firms <- data.frame(Firm_Final = unique(df_all_firms$Firm_Final))

# Create a full combination of all Firm_Final and Year pairs
complete_grid <- expand.grid(Firm_Final = complete_firms$Firm_Final, Year = complete_years$Year)

# Join with the original data and fill missing rows with NA
df_all_firms_complete <- complete_grid %>%
  left_join(df_all_firms, by = c("Firm_Final", "Year"))

```

## 5.6. Exclude firms that were always private
```{r}

df_all_firms <- df_all_firms_complete %>%
  filter(Privatization != 1)  # Filters rows where Privatization is not equal to 1

```


## 5.7. Graph of the Main Variables: Before and After Privatization
```{r}

# Reshape the data to long format
df_all_firms_long <- df_all_firms %>%
  pivot_longer(cols = c(SAIDI, SAIFI, debtequity_ratio, netprofit_margin, revenue, consumers, consumption, B1_RESIDENCIAL, B2_RURAL, B3_DEMAIS, B4a_REDE_DE_DISTRIBUICAO),
               names_to = "variable", 
               values_to = "value")

# Convert 'year_before_after' to numeric (with negative values allowed)
df_all_firms_long <- df_all_firms_long %>%
  mutate(year_before_after = as.numeric(gsub("[^0-9.-]", "", `year_before_after`)))  # Allow for negative signs


# Calculate the average of each variable for each year
df_all_firms_avg <- df_all_firms_long %>%
  group_by(year_before_after, variable) %>%
  summarise(avg_value = mean(value, na.rm = TRUE), .groups = "drop")

# Plot with geom_line for the average values
ggplot(df_all_firms_avg, aes(x = year_before_after, y = avg_value, color = variable, group = variable)) +
  geom_line() +  # Adds lines for each variable
  facet_wrap(~ variable, scales = "free_y") +  # Creates separate plots for each variable
  labs(
    title = "Average Time Series of Different Variables",
    x = "Year (Before/After)",
    y = "Average Value"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )

```


## 5.8. Correlation Matrix 
```{r}


# Convert character to numeric and compute log while handling zeros and warnings
df_all_firms <- df_all_firms %>%
  mutate(across(c(revenue, revenue_tax,netprofit_margin, consumption, consumers, tax, B1_RESIDENCIAL, B2_RURAL, B3_DEMAIS, B4a_REDE_DE_DISTRIBUICAO), 
                ~ log(as.numeric(.) + 1), .names = "log_{.col}"))  # Adding 1 to avoid log(0)



corrplot(corr = cor(df_all_firms[, c(4:11, 23:31)], use="pairwise.complete.obs"),
         addCoef.col = "white",
         number.cex = 0.8,
         number.digits = 1,
         diag = FALSE,
         #bg = "grey",
         outline = "black",
         addgrid.col = "white", 
         mar = c(1,1,1,1)) #pairwise.complete.obs, because there are too many NAs


GGally::ggpairs(df_all_firms[, c(4:11, 20, 23:31)],
                ggplot2::aes(colour = Treatment))


```


```{r 2.3.1. Variance Inflation Factor (VIF): PATENT TECHNOLOGIES}


reg_TEC <- plm(SAIFI ~ privatization_year + log_consumers + debtequity_ratio + netprofit_margin + B1_RESIDENCIAL, data = df_all_firms, model = "pooling", index = c("Firm_Final", "Year"))
  summary(reg_TEC)

#variance inflation factor (VIF), Test for Multicolinearity
vif(reg_TEC)

#Values of VIF under 5, GDP was excluded due to multicolineatiry

```

# Summary Statistics
```{r}

sumtable(df_all_firms, group = "Treatment", out = "htmlreturn", file = "balancetable3.htm")

```


```{r}

# df_all_firms <- df_all_firms %>%
#   mutate(treat = Treatment == "treated")  # Creates a logical column (TRUE/FALSE)


#transform "privatization_zear" into numeric to run the code
df_all_firms <- df_all_firms %>%
  mutate(privatization_year = as.numeric(privatization_year)) %>% 
  mutate(year_before_after = as.numeric(year_before_after))



```



# TwoWayFE - Callaway and Santanna 
```{r}

# Group Treatment: SAIFI
cs21 = att_gt(
    yname         = "SAIFI",
    tname         = "Year",
    idname        = "idname",
    gname         = "Privatization",
  # xformla       = NULL,            # No additional controls in this dataset
    control_group = "notyettreated", # Too few groups for "nevertreated" default
    clustervars   = "idname",
    data          = df_all_firms
    )
cs21


cs21_es = aggte(cs21, type = "dynamic", min_e = -10, max_e = 10, cband = FALSE)
cs21_es

ggdid(cs21_es, title = "(cs)did")



# Group Treatment: Net Profit Margin
cs21 = att_gt(
    yname         = "netprofit_margin",
    tname         = "Year",
    idname        = "idname",
    gname         = "Privatization",
  # xformla       = NULL,            # No additional controls in this dataset
    control_group = "notyettreated", # Too few groups for "nevertreated" default
    clustervars   = "idname",
    na.rm = TRUE,
    data          = df_all_firms
    )
cs21


cs21_es = aggte(cs21, 
                type = "dynamic", 
                min_e = -10, 
                max_e = 10, 
                cband = FALSE,
                na.rm = TRUE)
cs21_es

ggdid(cs21_es, title = "(cs)did")

```


# Package: did_multiplegt
```{r TwoWayFEWeights Chaisemartin, D'Haultfoeuille Package}

#Chaisemartin and D'Haultfoeuille recommend the first, to compute the weights attached to their regression and the ratio of |βbfe| divided by the standard deviation of the weights. If many weights are negative, and if the ratio is not very large, we recommend that they compute our new estimator.

#Estimation of the weights according to Chaisemartin and D'Haultfoeuille, using feTR = which estimates the weights and sensitivity measures attached to the fixed-effects regression under the common trends assumption
did_multiplegt(df = df_all_firms, Y = "SAIFI", G = "Firm_Final", T = "Year", D = "privatization_year", mode = "old")

#The result show not many negative weights, and not very large ratios, nevertheless we compute the DiD with multiple periods of Chaisemartin and D'Haultfoeuille, as a matter of robustness.

mod_dCDH20 = did_multiplegt(
  df_all_firms, 'SAIFI', 'Firm_Final', 'Year', 'privatization_year', # original regression params
  dynamic   = 5,                  # no. of post-treatment periods
  placebo   = 5,                  # no. of pre-treatment periods
  brep      = 20,                  # no. of bootstraps (required for SEs)
  cluster   = 'idname',                # variable to cluster SEs on
  parallel  = FALSE,                 # run the bootstraps in parallel
  mode = "old"
  )

```


# Package: did_multiplegt_dyn
```{r}

did_multiplegt_dyn(df = df_all_firms, 
                   outcome = "SAIFI", 
                   group = "Firm_Final", 
                   time = "Year", 
                   treatment = "privatization_year",
                   controls = c("log_consumers"))

did_saifi = did_multiplegt_dyn(
  df = df_all_firms, "SAIFI", "Firm_Final", "Year",  "privatization_year", # original regression params
  effects   = 5,                  # no. of post-treatment periods
  placebo   = 5,                  # no. of pre-treatment periods
  cluster   = 'Firm_Final',                 # variable to cluster SEs on
  controls = c("log_consumers")
  )

print(did_saifi)


```


```{r}

did_saidi = did_multiplegt_dyn(
  df = df_all_firms, "SAIDI", "Firm_Final", "Year",  "privatization_year", # original regression params
  effects   = 5,                  # no. of post-treatment periods
  placebo   = 5,                  # no. of pre-treatment periods
  cluster   = 'Firm_Final',                 # variable to cluster SEs on
  controls = c("log_consumers")
  )

print(did_saidi)

did_saifi = did_multiplegt_dyn(
  df = df_all_firms, "SAIFI", "Firm_Final", "Year",  "privatization_year", # original regression params
  effects   = 5,                  # no. of post-treatment periods
  placebo   = 5,                  # no. of pre-treatment periods
  cluster   = 'Firm_Final',                 # variable to cluster SEs on
  controls = c("log_consumers")
  )

print(did_saifi)


did_B1 = did_multiplegt_dyn(
  df = df_all_firms, "B1_RESIDENCIAL", "Firm_Final", "Year",  "privatization_year", # original regression params
  effects   = 5,                  # no. of post-treatment periods
  placebo   = 5,                  # no. of pre-treatment periods
  cluster   = 'Firm_Final',                 # variable to cluster SEs on
  controls = c("log_consumers")
  )

print(did_B1)



did_B1 = did_multiplegt_dyn(
  df = df_all_firms, "debtequity_ratio", "Firm_Final", "Year",  "privatization_year", # original regression params
  effects   = 5,                  # no. of post-treatment periods
  placebo   = 5,                  # no. of pre-treatment periods
  cluster   = 'Firm_Final',                 # variable to cluster SEs on
  controls = c("log_consumers")
  )

print(did_B1)


did_B1 = did_multiplegt_dyn(
  df = df_all_firms, "netprofit_margin", "Firm_Final", "Year",  "privatization_year", # original regression params
  effects   = 5,                  # no. of post-treatment periods
  placebo   = 5,                  # no. of pre-treatment periods
  cluster   = 'Firm_Final',                 # variable to cluster SEs on
  controls = c("log_consumers")
  )

print(did_B1)


df_all_firms_test <- df_all_firms %>%
  mutate(idname = as.integer(factor(Firm_Final)))  # Ensures unique IDs

```



# 4. Difference-in-difference implementation
```{r OLS Regression Models: PATENT H}

#SAIDI
reg_saidi <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_saidi)

#SAIFI
reg_saifi <- plm(SAIFI ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_saifi)


#PROFIT
reg_profit <- plm(netprofit_margin ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_profit)


#DEBIT
reg_debit <- plm(debtequity_ratio ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_debit)

#consumers
reg_consumers <- plm(consumers ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_consumers)


#consumption
reg_consumption <- plm(consumption ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_consumption)

#revenue
reg_revenue <- plm(revenue ~ privatization_year, data = df_all_firms, model = "pooling",
                   index = c("Firm_Final", "Year"))
summary(reg_revenue)


```


```{r TWO-WAY FIXED EFFECTS}

#SAIDI
twoway_H <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "within", effect = "twoway",
                 index = c("Firm_Final", "Year"))
summary(twoway_H)


#SAIFI
twoway_H <- plm(SAIFI ~ privatization_year, data = df_all_firms, model = "within", effect = "twoway",
                 index = c("Firm_Final", "Year"))
summary(twoway_H)

#PROFIT
reg_profit <- plm(netprofit_margin ~ privatization_year, data = df_all_firms, model = "within", effect = "twoway",
                   index = c("Firm_Final", "Year"))
summary(reg_profit)


#DEBIT
reg_debit <- plm(debtequity_ratio ~ privatization_year, data = df_all_firms,  model = "within", effect = "twoway",
                   index = c("Firm_Final", "Year"))
summary(reg_debit)

#consumers
reg_consumers <- plm(consumers ~ privatization_year, data = df_all_firms,  model = "within", effect = "twoway",
                   index = c("Firm_Final", "Year"))
summary(reg_consumers)


#consumption
reg_consumption <- plm(consumption ~ privatization_year, data = df_all_firms, model = "within", effect = "twoway",
                   index = c("Firm_Final", "Year"))
summary(reg_consumption)

#revenue
reg_revenue <- plm(revenue ~ privatization_year, data = df_all_firms, model = "within", effect = "twoway",
                   index = c("Firm_Final", "Year"))
summary(reg_revenue)

```



```{r Test: OLS regression OR fixed effect model? - PATENTS H}
#Test for poolability of data: pFtest(PATENTS H)
#all patents h, all controls

did_reg_saidi_with <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "within", 
                 index = c("Firm_Final", "Year"))

did_reg_saidi_pool <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "pooling", 
                 index = c("Firm_Final", "Year"))

pFtest(did_reg_saidi_with,did_reg_saidi_pool)

```

```{r TIME FIXED EFFECTS}

reg_saidi_FEtime <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "within", effect = "time", index = c("Firm_Final", "Year"))
summary(reg_saidi_FEtime)

```

```{r COUNTRY FIXED EFFECTS}

reg_saidi_FEcountry <- plm(SAIDI ~ privatization_year, data = df_all_firms, model = "within", effect = "individual", index = c("Firm_Final", "Year"))
summary(reg_saidi_FEcountry)
```

```{r TWO-WAY FIXED EFFECTS}

twoway_H <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ihs_GDPfull + ElecConsumption, data = base, model = "within", effect = "twoway",
                 index = c("country", "Year"))
summary(twoway_H)

twoway_H <- plm(patents_H_application ~ RDI_regulation, data = base, model = "within", 
                effect = "twoway",
                index = c("country", "Year"))
                summary(twoway_H)

```

```{r Testing for FIXED OR RANDOM}
#FIXED
fixed_H <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ElecConsumption + ihs_GDPfull, data=base, index=c("country", "Year"), model="within")
summary(fixed_H)

# Display the fixed effects (constants for each country)
fixef(fixed_H)    

# Testing for fixed effects, null: OLS better than fixed
pFtest(fixed_H, reg_H_app_5)

#RANDOM
random_H <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ElecConsumption + ihs_GDPfull, data=base, index=c("country", "Year"), model="random")
summary(random_H)

#FIXED OR RANDOM: Hausman test
phtest(fixed_H, random_H)

#Testing for time-fixed effects
fixed_H_time <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ElecConsumption + ihs_GDPfull + factor(Year), data=base, index=c("country", "Year"), model="within")
summary(fixed_H_time)

pFtest(fixed_H_time, fixed_H)

plmtest(fixed_H, c("time"), type=("bp"))
#time fixed as well as unit fixed effects are present, hence two-way FE model is to be chosen#

```

```{r Model Test: Serial correlation, heteroskedacity}
#FINAL TWO Way FE Model#
did_reg_H <- plm(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ihs_GDPfull + ElecConsumption, data = base, model = "within", effect = "twoway",
                 index = c("country", "Year"))
summary(did_reg_H)

# Pasaran CD (cross-sectional dependence) test reveals NO cross-sectional dependence#
pcdtest(did_reg_H, test = c("cd"))

#Testing for serial correlation, reveals serial correlation!#*
pbgtest(did_reg_H)

#Testing for unit roots/stationarity reveals no unit root present#
Panel.set <- pdata.frame(base, index = c("country", "Year"))

adf.test(Panel.set$patents_H_application, k=2)

#  Breusch-Pagan for heteroskedasticity*
bptest(patents_H_application ~ RDI_regulation + Personnel + Budget + ValueRegulation + ElecConsumption + ihs_GDPfull + factor(country), data = base, studentize=F)

#Estimation with cluster robust standard errors#

coeftest(did_reg_H, 
         vcov = vcovHC(did_reg_H, 
                       method = "arellano",
                       cluster = "group",
                       type="HC0"))

```

